A New Model to Predict Survival in Patients with End-Stage Liver Disease

### 2022-07-03 analysis/article.Rmd
feat: round spearman correlation to 2 digits

Our model, AMELD, uses `r length(cfs)` predictors.
Half of them, INR, (direct) bilirubin, and cystatin C are identical
or similar to the labortory measurements utilized in the classical MELD.
The direct bilirubin selected by our approach and the total bilirubin in MELD
are highly correlated (spearman correlation:
`r round(cor(amelddata$x, method = "spearman")["BILI_S", "BILID_S"])`) and
therefore interchangeable.

>>>>

Our model, AMELD, uses `r length(cfs)` predictors.
Half of them, INR, (direct) bilirubin, and cystatin C are identical
or similar to the labortory measurements utilized in the classical MELD.
The direct bilirubin selected by our approach and the total bilirubin in MELD
are highly correlated (spearman correlation:
`r round(cor(amelddata$x, method = "spearman")["BILI_S", "BILID_S"], 2)`) and
therefore interchangeable.
